---
title: "Experiments EDA with synthview"
author: "MIKE MERRY"
date: "7/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(jsonlite)
library(GGally)           # Load GGally package
library(stargazer)


genRecords_raw <- read.csv('./../data/processed/2019-07-26/generationRecords.csv') 
genRecords <- genRecords_raw %>% as_tibble() %>%
 mutate(generationDuration = generationEndTime - generationStartTime,
     reproductionDuration = reproductionEndTime - reproductionStartTime,
     backpropDuration = backpropEndTime - backpropStartTime
 )

genRecords <- genRecords %>%
  left_join(
    genRecords %>%
      group_by(dataset,
               experimentType,
               experimentValue,
               experimentIteration) %>%
      summarise(experimentStartTime = min(generationStartTime),
                experimentMinMaxFitness = min(fitnessMean)),
    by=c("dataset", "experimentValue", "experimentIteration", "experimentType")
    )

results_raw <- read.csv('./../data/processed/2019-07-26/results.csv')



results_iris <- results_raw %>% filter(dataset== 'iris') %>% as_tibble() %>%
 mutate(X0 = gsub("\\[", "", X0),
     X0 = gsub("\\]", "", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = trimws(X0),
     X2 = gsub("\\[", "", X2),
     X2 = gsub("\\]", "", X2),
     X2 = gsub("  ", " ", X2)
     ) %>%
 separate(X0,c('sepal.length',
 'sepal.width',
 'petal.length',
 'petal.width'), sep=" ", remove = FALSE) %>%
 separate(X2,c('p0',
 'p1',
 'p2'), sep=", ", remove = FALSE) %>%
 mutate(
  sepal.length = as.numeric(sepal.length),
  sepal.width = as.numeric(sepal.width),
  petal.length = as.numeric(petal.length),
  petal.width = as.numeric(petal.width),
  p0 = as.numeric(p0),
  p1 = as.numeric(p1),
  p2 = as.numeric(p2),
  maxPred = pmax(p0, p1, p2),
  pred = case_when(p0 == maxPred ~ 0,
           p1 == maxPred ~ 1,
           p2 == maxPred ~ 2))


iris_dataset <- results_iris %>%
  filter(experimentType == 'population',
         experimentValue == 5,
         experimentIteration == 0) %>%
  select(contains('sepal'),
         contains('petal'),
         X1,
         X)

results_iris <- results_iris %>%
  select(-X1, 
         -contains('sepal'),
         -contains('petal')) %>%
  left_join(iris_dataset, by='X') %>%
  mutate(
  correct = pred == X1,
  pred = as.factor(pred))


numericcharacters <- function(x) {
  !any(is.na(suppressWarnings(as.numeric(x)))) & is.character(x)
}

results_bc <- results_raw %>% filter(dataset== 'breast-cancer') %>% as_tibble() %>%
 mutate(X0 = gsub("\\[", "", X0),
     X0 = gsub("\\]", "", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = trimws(X0),
     X2 = gsub("\\[", "", X2),
     X2 = gsub("\\]", "", X2),
     X2 = gsub("  ", " ", X2),
     X2 = as.numeric(X2),
     pred = round(X2),
     correct = pred==X1
     ) %>%
 separate(X0,c('mean radius', 'mean texture', 'mean perimeter', 'mean area',
       'mean smoothness', 'mean compactness', 'mean concavity',
       'mean concave points', 'mean symmetry', 'mean fractal dimension',
       'radius error', 'texture error', 'perimeter error', 'area error',
       'smoothness error', 'compactness error', 'concavity error',
       'concave points error', 'symmetry error',
       'fractal dimension error', 'worst radius', 'worst texture',
       'worst perimeter', 'worst area', 'worst smoothness',
       'worst compactness', 'worst concavity', 'worst concave points',
       'worst symmetry', 'worst fractal dimension'), sep=" ", remove = FALSE) %>%
  mutate_if(numericcharacters,as.numeric)



results_sv <- results_raw %>% filter(dataset== 'synthview') %>% as_tibble() %>%
 mutate(X0 = gsub("\\[", "", X0),
     X0 = gsub("\\]", "", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = trimws(X0),
     X2 = gsub("\\[", "", X2),
     X2 = gsub("\\]", "", X2),
     X2 = gsub("  ", " ", X2),
     X2 = as.numeric(X2),
     pred = round(X2),
     correct = pred==X1
     ) 

```

```{r}
results_bc %>%
  head
```


```{r}
results_sv %>%
  head
```


```{r}
results_iris%>%
  filter(experimentType == 'epochs') %>%
  glimpse
```
# Can this achieve good predictive performance?

## IRIS
On the Iris dataset, best performances are >95%, and best I've seen (overfit?) is 98%
```{r}
results_iris %>%
  group_by(experimentType,
           experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  arrange(-accuracy) %>%
  View
```
For the different experiments, the key thing is that `epochs` had a much longer run time for nGenerations
```{r}
results_iris %>%
  group_by(experimentType,
           experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  ggplot(aes(experimentType, accuracy)) +
  geom_boxplot() +
  ylim(0, 1)
```

```{r}
genRecords %>%
  filter(dataset == 'iris') %>%
  group_by(experimentType,
           experimentValue, 
           experimentIteration) %>%
  summarise(maxFitness = max(fitnessMax),
            maxMeanFitness = max(fitnessMean),
            nGenerations = max(generation)) %>%
  ggplot(aes(nGenerations, 
             maxFitness,
             group=nGenerations)) +
  geom_boxplot()
```
```{r}
genRecords %>%
  filter(dataset == 'iris') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=interaction(experimentType, experimentValue), 
             group = interaction(experimentType, experimentValue, experimentIteration))) +
  geom_point() +
  geom_line() +
  facet_grid(experimentType~.)
```
So who was the best performance?
```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  summarise(max(fitnessMax))
```

```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```

## Breast Cancer

Do we see the same trends?

```{r}
genRecords %>%
  filter(dataset == 'breast-cancer') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=interaction(experimentType, experimentValue), 
             group = interaction(experimentType, experimentValue, experimentIteration))) +
  geom_point() +
  geom_line() +
  facet_grid(experimentType~.)
```
Yes, primarily that we need large enough population. Unfortunately, epochs experiment failed for `breast-cancer`, so we can't see the results there.

```{r}
genRecords %>%
  filter(dataset == 'breast-cancer') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
Yes, similar patterns

# Does num. epochs/generation change training?

The question is, whether or not the epochs are critical for training, or whether or not generations are more important.

All experiments were with the same number of generations, varying number of epochs
```{r}
results_iris %>%
  filter(experimentType == 'epochs') %>%
  group_by(experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  ggplot(aes(experimentValue, accuracy)) +
  geom_point() +
  xlim(0, 150) +
  ylim(0, 1)
```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  group_by(experimentIteration, experimentValue) %>%
  summarise(fitness = max(fitnessMax))
```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  group_by(experimentIteration, experimentValue) %>%
  summarise(fitness = max(fitnessMax)) %>%
  ggplot(aes(experimentValue, fitness)) +
  geom_point() +
  ylim(1, 1.6)

```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  ggplot(aes(generation, fitnessMax, color=as.factor(experimentValue), group = generation)) +
  geom_boxplot() +
  facet_grid(experimentValue~.)

```
Really, there is no difference from the number of epochs. Generations (and topological variation) is the key element

# How do they train?

```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10, 50),
         experimentIteration %in% c(0, 3, 4)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```

# What about speed of training?

```{r}

genRecords %>%
 group_by(dataset,
          experimentType,
      experimentValue,
      generation) %>%
  filter(dataset=='iris') %>%
 summarise(backpropDurationMean = mean(backpropDuration),
      backpropDurationSD = sd(backpropDuration)) %>%
 ggplot(aes(experimentValue, backpropDurationMean)) +
 geom_point() + 
  facet_grid(experimentType~.) +
    geom_smooth(method='lm',formula=y~x) +
  ggtitle("BP Duration against population size - Iris")
```

## GPU vs CPU

```{r}

genRecords %>%
 group_by(dataset,
          experimentType,
      experimentValue,
      generation) %>%
  filter(experimentType %in% c('population', 'populationgpu')) %>%
 summarise(backpropDurationMean = mean(backpropDuration),
      backpropDurationSD = sd(backpropDuration)) %>%
 ggplot(aes(experimentValue, 
            backpropDurationMean,
            color=experimentType)) +
 geom_point() + 
  facet_grid(dataset~.) +
    geom_smooth(method='lm',formula=y~x) +
  ggtitle("BP Duration against population size - Iris")
```
GPU is significantly sllower on both datasets, but still looking good with a linear relationship

# Next experiments

* Population size
* Synthetic View



```{r}
genRecords %>%
  group_by(dataset,
           experimentType,
           experimentValue) %>%
  filter(!dataset=='breast-cancer') %>%
  summarise(maxFitness = max(fitnessMax, na.rm = TRUE),
            maxFitnessSD = sd(fitnessMax, na.rm = TRUE))
```

```{r}
genRecords %>%
  filter(dataset == 'synthview') %>%
  ggplot(aes(generation, 
             fitnessMax, 
             group = interaction(experimentValue, experimentIteration),
             color=as.factor(experimentValue))) +
  geom_point() +
  geom_line() + 
  ylim(0.9, 0.95)
```

```{r}
results_sv %>%
  group_by(experimentValue, experimentIteration) %>%
  summarise(n=n())
```



```{r}
genRecords %>%
  group_by(dataset) %>%
  summarise(maxFitness = max(fitnessMax, na.rm = TRUE))
```


# For paper

```{r}
genRecords %>%
  filter(dataset == 'iris') %>%
  group_by(experimentType,
           dataset) %>%
  summarise(n=n())
```

```{r}
genRecords %>%colnames()
```

```{r}
genRecords %>%
  filter(experimentType == 'population') %>%
  group_by(dataset,
           experimentValue) %>%
  summarise(n=n(),
            maxMeanFitness = max(fitnessMean),
            meanFitness = mean(fitnessMean),
            bpTime = mean(backpropDuration),
            bpSD = sd(backpropDuration),
            gaTime = mean(reproductionDuration),
            gaSD = sd(reproductionDuration),
            ) %>%
  mutate_if(is.numeric, round, 3) %>%
  select(-n) %>%
  as.tibble() %>%
  stargazer(., summary = FALSE)
  
```
## Experiment 1

```{r}
genRecords %>%
  filter(experimentType == 'population',
         dataset=='iris') %>%
  group_by(experimentValue, generation) %>%
  summarise(maxFit = max(fitnessMean),
            minFit = min(fitnessMean),
            meanFit = mean(fitnessMean)) %>%
  ggplot(aes(generation, 
             meanFit, 
             linetype=as.factor(experimentValue),
             color=as.factor(experimentValue), 
             group=interaction(experimentValue))) +
    geom_ribbon(aes(ymin=minFit, ymax=maxFit, fill=as.factor(experimentValue)), alpha=0.3 )+
  # geom_point() + 
  geom_line() +
  labs(x='Generation',
       y='Fitness',
       color='Population Size',
       linetype='Population Size',
       fill='Population Size')

  ggsave('./../data/processed/aaai_paper/fitness_over_generation_pop_exp_1.pdf', device='pdf', width=5, height=2.5)

```

```{r}
genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime,
         fitnessGain = fitnessMean - experimentMinMaxFitness) %>%
  filter(experimentType == 'population') %>% 
  group_by(dataset,
           generation,
           experimentValue) %>%
  filter(generation==19) %>%
  summarise(meanRunTime = mean(experimentRunTime), 
            sdRunTime = sd(experimentRunTime),
            meanFitnessGain = mean(fitnessGain),
            sdFitnessGain = sd(fitnessGain),
            
            meanGainPerSecond = mean(fitnessGain/experimentRunTime*100000000),
            sdGainPerSecond = sd(fitnessGain/experimentRunTime*100000000)) %>%
  select(experimentValue,
         meanRunTime,
         sdRunTime,
         meanGainPerSecond,
         sdGainPerSecond) %>%
    mutate_if(is.numeric, round, 1) %>%
  as.tibble() %>%
  select(-generation) %>%
  stargazer(., summary = FALSE)
```

```{r}
genRecords %>%
  group_by(dataset,
           experimentType,
           experimentValue) %>%
  summarise(n=n())
```


## Experiment 2


```{r}

genRecords %>%
  group_by(dataset,
           experimentType,
           experimentValue,
           experimentIteration) %>%
  summarise(experimentStartTime = min(generationStartTime)) %>%
  filter(experimentType == 'epochs')
```


```{r}
 genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime) %>%
  filter(experimentType == 'epochs') %>% 
  group_by(experimentValue, generation) %>%
  summarise(meanMaxFitness = mean(fitnessMax),
            sdMaxFitness = sd(fitnessMax),
            maxMaxFitness = max(fitnessMax),
            minMaxFitness = min(fitnessMax),
            meanRunTime = mean(experimentRunTime)) %>%
  ggplot(aes(meanRunTime, 
             meanMaxFitness, 
             color=as.factor(experimentValue),
             group=interaction(experimentValue))) + 
  geom_ribbon(aes(ymin = minMaxFitness, ymax = maxMaxFitness, fill=as.factor(experimentValue)), alpha = 0.2) + 
  geom_point() + 
  geom_line()
```

```{r}
 genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime) %>%
  filter(experimentType == 'epochs') %>% 
  ggplot(aes(experimentRunTime, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentValue, experimentIteration))) + 
  geom_point() + 
  geom_line()
```

```{r}
genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime,
         fitnessGain = fitnessMean - experimentMinMaxFitness) %>%
  filter(experimentType == 'epochs') %>% 
  group_by(generation,
           experimentValue) %>%
  summarise(meanRunTime = mean(experimentRunTime), 
            sdRunTime = sd(experimentRunTime),
            meanFitnessGain = mean(fitnessGain),
            sdFitnessGain = sd(fitnessGain)) %>%
  ggplot(aes(generation, 
             meanFitnessGain, 
             group=experimentValue, 
             color=as.factor(experimentValue))) + 
  geom_line() +
  labs(title='Fitness gain over generations', 
       x='Generation',
       y='Mean fitness gain',
       color='Epochs/generation') + 
  theme(legend.position = c(0.8, 0.4))


  ggsave('./../data/processed/aaai_paper/fitness_gain_over_generations_pops.pdf', device='pdf', width=5, height=5)
            
```
```{r}
genRecords %>%
  group_by(dataset,
           experimentType) %>%
  summarise(mean(genomeNodeSizesMean),
            mean(genomeConnectionSizesMean))
```

```{r}
genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime,
         fitnessGain = fitnessMean - experimentMinMaxFitness) %>%
  filter(experimentType == 'epochs') %>% 
  View
  group_by(generation,
           experimentValue) %>%
  summarise(meanRunTime = mean(experimentRunTime), 
            sdRunTime = sd(experimentRunTime),
            meanFitnessGain = mean(fitnessGain),
            sdFitnessGain = sd(fitnessGain)) %>%
  ggplot(aes(meanRunTime, 
             meanFitnessGain, 
             group=experimentValue, 
             color=as.factor(experimentValue))) + 
  geom_line() +
  labs(title='Fitness gain over time (s)', 
       x='Run time (s)',
       y='Mean fitness gain',
       color='Epochs/generation') + 
  theme(legend.position = c(0.8, 0.4))


  ggsave('./../data/processed/aaai_paper/fitness_gain_over_time_pops.pdf', device='pdf', width=5, height=5)
            
```
```{r}
genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime,
         fitnessGain = fitnessMean - experimentMinMaxFitness) %>%
  filter(experimentType == 'epochs') %>% 
  group_by(generation,
           experimentValue) %>%
  filter(generation==49) %>%
  summarise(meanRunTime = mean(experimentRunTime), 
            sdRunTime = sd(experimentRunTime),
            meanFitnessGain = mean(fitnessGain),
            sdFitnessGain = sd(fitnessGain),
            
            meanGainPerSecond = mean(fitnessGain/experimentRunTime*100000000),
            sdGainPerSecond = sd(fitnessGain/experimentRunTime*100000000)) %>%
  select(experimentValue,
         meanRunTime,
         sdRunTime,
         meanGainPerSecond,
         sdGainPerSecond) %>%
    mutate_if(is.numeric, round, 1) %>%
  as.tibble() %>%
  select(-generation) %>%
  stargazer(., summary = FALSE)
```

```{r}
genRecords %>%
  mutate(experimentRunTime = generationEndTime - experimentStartTime,
         fitnessGain = fitnessMean - experimentMinMaxFitness) %>%
  filter(experimentType %in% c('population', 'populationgpu')) %>%
  group_by(dataset, 
           experimentValue,
           experimentType, ) %>%
  filter(experimentValue < 15) %>%
  summarise(n=n(),
            maxMeanFitness = max(fitnessMean),
            meanFitness = mean(fitnessMean),
            bpTime = mean(backpropDuration),
            bpSD = sd(backpropDuration),
            gaTime = mean(reproductionDuration),
            gaSD = sd(reproductionDuration),) %>%
  select(dataset,
         experimentValue,
         experimentType,
         bpTime,
         bpSD) %>%
    mutate_if(is.numeric, round, 1) %>%
    as.tibble() %>%
  stargazer(., summary=FALSE)
```

