---
title: "EDA of Epochs and GPU"
author: "MIKE MERRY"
date: "7/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(jsonlite)
library("GGally")           # Load GGally package

genRecords <- read.csv('./../data/processed/generationRecords.csv') 
genRecords <- genRecords %>% as_tibble() %>%
 mutate(generationDuration = generationEndTime - generationStartTime,
     reproductionDuration = reproductionEndTime - reproductionStartTime,
     backpropDuration = backpropEndTime - backpropStartTime
 )

results_raw <- read.csv('./../data/processed/results.csv')



results_iris <- results_raw %>% filter(dataset== 'iris') %>% as_tibble() %>%
 mutate(X0 = gsub("\\[", "", X0),
     X0 = gsub("\\]", "", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = trimws(X0),
     X2 = gsub("\\[", "", X2),
     X2 = gsub("\\]", "", X2),
     X2 = gsub("  ", " ", X2)
     ) %>%
 separate(X0,c('sepal.length',
 'sepal.width',
 'petal.length',
 'petal.width'), sep=" ", remove = FALSE) %>%
 separate(X2,c('p0',
 'p1',
 'p2'), sep=", ", remove = FALSE) %>%
 mutate(
  sepal.length = as.numeric(sepal.length),
  sepal.width = as.numeric(sepal.width),
  petal.length = as.numeric(petal.length),
  petal.width = as.numeric(petal.width),
  p0 = as.numeric(p0),
  p1 = as.numeric(p1),
  p2 = as.numeric(p2),
  maxPred = pmax(p0, p1, p2),
  pred = case_when(p0 == maxPred ~ 0,
           p1 == maxPred ~ 1,
           p2 == maxPred ~ 2))


iris_dataset <- results_iris %>%
  filter(experimentType == 'population',
         experimentValue == 5,
         experimentIteration == 0) %>%
  select(contains('sepal'),
         contains('petal'),
         X1,
         X)

results_iris <- results_iris %>%
  select(-X1, 
         -contains('sepal'),
         -contains('petal')) %>%
  left_join(iris_dataset, by='X') %>%
  mutate(
  correct = pred == X1,
  pred = as.factor(pred))


numericcharacters <- function(x) {
  !any(is.na(suppressWarnings(as.numeric(x)))) & is.character(x)
}

results_bc <- results_raw %>% filter(dataset== 'breast-cancer') %>% as_tibble() %>%
 mutate(X0 = gsub("\\[", "", X0),
     X0 = gsub("\\]", "", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = gsub("  ", " ", X0),
     X0 = trimws(X0),
     X2 = gsub("\\[", "", X2),
     X2 = gsub("\\]", "", X2),
     X2 = gsub("  ", " ", X2),
     X2 = as.numeric(X2),
     pred = round(X2),
     correct = pred==X1
     ) %>%
 separate(X0,c('mean radius', 'mean texture', 'mean perimeter', 'mean area',
       'mean smoothness', 'mean compactness', 'mean concavity',
       'mean concave points', 'mean symmetry', 'mean fractal dimension',
       'radius error', 'texture error', 'perimeter error', 'area error',
       'smoothness error', 'compactness error', 'concavity error',
       'concave points error', 'symmetry error',
       'fractal dimension error', 'worst radius', 'worst texture',
       'worst perimeter', 'worst area', 'worst smoothness',
       'worst compactness', 'worst concavity', 'worst concave points',
       'worst symmetry', 'worst fractal dimension'), sep=" ", remove = FALSE) %>%
  mutate_if(numericcharacters,as.numeric)

```

```{r}
results_iris%>%
  filter(experimentType == 'epochs') %>%
  glimpse
```
# Can this achieve good predictive performance?

## IRIS
On the Iris dataset, best performances are >95%, and best I've seen (overfit?) is 98%
```{r}
results_iris %>%
  group_by(experimentType,
           experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  arrange(-accuracy)
```
For the different experiments, the key thing is that `epochs` had a much longer run time for nGenerations
```{r}
results_iris %>%
  group_by(experimentType,
           experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  ggplot(aes(experimentType, accuracy)) +
  geom_boxplot() +
  ylim(0, 1)
```

```{r}
genRecords %>%
  filter(dataset == 'iris') %>%
  group_by(experimentType,
           experimentValue, 
           experimentIteration) %>%
  summarise(maxFitness = max(fitnessMax),
            maxMeanFitness = max(fitnessMean),
            nGenerations = max(generation)) %>%
  ggplot(aes(nGenerations, 
             maxFitness,
             group=nGenerations)) +
  geom_boxplot()
```
```{r}
genRecords %>%
  filter(dataset == 'iris') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=interaction(experimentType, experimentValue), 
             group = interaction(experimentType, experimentValue, experimentIteration))) +
  geom_point() +
  geom_line() +
  facet_grid(experimentType~.)
```
So who was the best performance?
```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  summarise(max(fitnessMax))
```

```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```

## Breast Cancer

Do we see the same trends?

```{r}
genRecords %>%
  filter(dataset == 'breast-cancer') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=interaction(experimentType, experimentValue), 
             group = interaction(experimentType, experimentValue, experimentIteration))) +
  geom_point() +
  geom_line() +
  facet_grid(experimentType~.)
```
Yes, primarily that we need large enough population. Unfortunately, epochs experiment failed for `breast-cancer`, so we can't see the results there.

```{r}
genRecords %>%
  filter(dataset == 'breast-cancer') %>%
  ggplot(aes(generation, 
             fitnessMean, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
Yes, similar patterns

# Does num. epochs/generation change training?

The question is, whether or not the epochs are critical for training, or whether or not generations are more important.

All experiments were with the same number of generations, varying number of epochs
```{r}
results_iris %>%
  filter(experimentType == 'epochs') %>%
  group_by(experimentValue,
           experimentIteration) %>%
  summarise(accuracy = mean(correct)) %>%
  ggplot(aes(experimentValue, accuracy)) +
  geom_point() +
  xlim(0, 150) +
  ylim(0, 1)
```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  group_by(experimentIteration, experimentValue) %>%
  summarise(fitness = max(fitnessMax))
```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  group_by(experimentIteration, experimentValue) %>%
  summarise(fitness = max(fitnessMax)) %>%
  ggplot(aes(experimentValue, fitness)) +
  geom_point() +
  ylim(1, 1.6)

```

```{r}
genRecords %>%
  filter(dataset == 'iris',
         experimentType == 'epochs') %>%
  ggplot(aes(generation, fitnessMax, color=as.factor(experimentValue), group = generation)) +
  geom_boxplot() +
  facet_grid(experimentValue~.)

```
Really, there is no difference from the number of epochs. Generations (and topological variation) is the key element

# How do they train?

```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10, 50),
         experimentIteration %in% c(0, 3, 4)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```
```{r}
genRecords %>%
  filter(dataset == 'iris', 
         experimentType == 'epochs',
         experimentValue %in% c(10),
         experimentIteration %in% c(3)) %>%
  ggplot(aes(generation, 
             fitnessMax, 
             color=as.factor(experimentValue),
             group=interaction(experimentIteration, experimentValue))) +
  geom_point() +
  geom_line()
```

# What about speed of training?

```{r}

genRecords %>%
 group_by(dataset,
          experimentType,
      experimentValue,
      generation) %>%
  filter(dataset=='iris') %>%
 summarise(backpropDurationMean = mean(backpropDuration),
      backpropDurationSD = sd(backpropDuration)) %>%
 ggplot(aes(experimentValue, backpropDurationMean)) +
 geom_point() + 
  facet_grid(experimentType~.) +
    geom_smooth(method='lm',formula=y~x) +
  ggtitle("BP Duration against population size - Iris")
```

## GPU vs CPU

```{r}

genRecords %>%
 group_by(dataset,
          experimentType,
      experimentValue,
      generation) %>%
  filter(experimentType %in% c('population', 'populationgpu')) %>%
 summarise(backpropDurationMean = mean(backpropDuration),
      backpropDurationSD = sd(backpropDuration)) %>%
 ggplot(aes(experimentValue, 
            backpropDurationMean,
            color=experimentType)) +
 geom_point() + 
  facet_grid(dataset~.) +
    geom_smooth(method='lm',formula=y~x) +
  ggtitle("BP Duration against population size - Iris")
```
GPU is significantly sllower on both datasets, but still looking good with a linear relationship

# Next experiments

* Population size
* Synthetic View






