---
title: "UCI - Adult - EDA"
author: "Mike Merry"
date: "10/05/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyr)
library(dplyr)
library(readr)
library(ggplot2)
library(modelr)
library(broom)
library(naivebayes)

adult.raw <- read.csv('./../../../data/uci/processed/data/adult/adult.data', 
                      col.names = c(
                        'age',
                        'workingClass',
                        'fnlwgt',
                        'education',
                        'educationNum',
                        'martialStatus',
                        'occupation',
                        'relationship',
                        'race',
                        'sex',
                        'capitalGain',
                        'capitalLoss',
                        'hoursPerWeek',
                        'nativeCountry',
                        'gt50k'
                        
                      )) 

adult <- adult.raw %>%
  mutate(gt50k = grepl('>50K', as.character(gt50k)))
```
age: continuous.
workclass: Private, Self-emp-not-inc, Self-emp-inc, Federal-gov, Local-gov, State-gov, Without-pay, Never-worked.
fnlwgt: continuous.
education: Bachelors, Some-college, 11th, HS-grad, Prof-school, Assoc-acdm, Assoc-voc, 9th, 7th-8th, 12th, Masters, 1st-4th, 10th, Doctorate, 5th-6th, Preschool.
education-num: continuous.
marital-status: Married-civ-spouse, Divorced, Never-married, Separated, Widowed, Married-spouse-absent, Married-AF-spouse.
occupation: Tech-support, Craft-repair, Other-service, Sales, Exec-managerial, Prof-specialty, Handlers-cleaners, Machine-op-inspct, Adm-clerical, Farming-fishing, Transport-moving, Priv-house-serv, Protective-serv, Armed-Forces.
relationship: Wife, Own-child, Husband, Not-in-family, Other-relative, Unmarried.
race: White, Asian-Pac-Islander, Amer-Indian-Eskimo, Other, Black.
sex: Female, Male.
capital-gain: continuous.
capital-loss: continuous.
hours-per-week: continuous.
native-country
```{r}
adult %>%
  glimpse
```



```{r}
adult %>%
  ggplot(aes(age, fill=gt50k)) + 
  geom_histogram(binwidth=2.5)
```
```{r}
adult %>%
  ggplot(aes(hoursPerWeek, fill=gt50k)) +
  geom_histogram()
```

```{r}
model <- lm(gt50k ~ ., data = adult)
```


```{r}
augmented <- add_residuals(add_predictions(adult, model), model)
```
```{r}
augmented %>%
  ggplot(aes(pred,fill=gt50k)) + 
  geom_histogram(binwidth=0.05)
```
```{r}
augmented %>%
  mutate(predbin = cut_width(pred, 0.05, center = 0.025)) %>%
  group_by(predbin) %>%
  summarise(n=n(),
            prop.gt50k = mean(gt50k)) 
```





```{r}
summary(model)
```

```{r}
cor(data.frame(cbind(actuals=augmented$gt50k, predicteds=augmented$pred)))
```

```{r}
augmented %>%
  write_csv('./../../phd-neat-experiments/data/processed/adult_linear_model_with_predictions.csv')
```

```{r}
nb <- naive_bayes(gt50k ~ ., data = adult)
```


```{r}
augment_columns(nb, adult) %>%
  mutate(pred = .fitted==2,
         correct = pred==gt50k) %>%
  summarise(mean(correct))

```

