---
title: "Comparison analysis"
author: "MIKE MERRY"
date: '2022-09-25'
output: html_document
---

```{r setup, include=FALSE}
  
knitr::opts_chunk$set(echo = TRUE)
require("tidyverse")
library(pROC)
# experiment_sha <- "24c00ce9" # 24088379
# experiment_sha <- "b53e57d1" 
# experiment_sha <- "24088379"
# experiment_sha <- "b4c86de1"
# experiment_sha <- "4bcfe941"

sha_file <- "./sha_file.json"
sha_doc <- rjson::fromJSON(file=sha_file)
config_doc <- rjson::fromJSON(file="./all_data_benchmarking_experiment_config.json")
experiment_sha <- sha_doc$sha
experiment_sha <- "3d382b80"
experiment_sha <- "1dd408e3"
experiment_sha <- "ba05ec6c"
experiment_sha <- "305afb53"
# dataset_name <- "GAMETES_Epistasis_3_Way_20atts_0.2H_EDM_1_1"

# dataset_name <- "breast_cancer_wisconsin"
codename <- config_doc$experiment$codename

```

```{r}

datasets_metadata_file <- "./datasets_metadata.json"
datasets_metadata <- jsonlite::fromJSON(datasets_metadata_file)

datasets_metadata %>%
  view
```


```{r}
compute_auc <- function(preds){
    my_tib<-tibble(y_test, preds)
    my_roc <- roc(my_tib, y, preds)
    return(as.numeric(my_roc$auc[[1]]))
}
compute_roc <- function(preds){
    my_tib<-tibble(y_test, preds)
    return(roc(my_tib, y, preds))
}
```


```{r}
experiment_sha
```


# Data ingest

```{r}
# results <- read_csv("./../../data/experiments/tests/data/resultsDatabase.csv")
# results <- read_csv("./../../data/experiments/tests/data/resultsDatabase_mlrig.csv")
results <- read_csv("./../../../mount_remote_phd/processed/resultsDatabase.csv") %>%
  rename("id" = "_id")

# results %>% filter(experimentSha == experiment_sha) %>%
#   select(-value) %>%View

```

```{r}
datasets <- unique(results %>%
                     filter(
                     experimentSha == experiment_sha) %>%
                     .$dataset)
datasets
```


```{r, echo = FALSE, results = 'hide', message = FALSE}

for(dataset_name in datasets){
  
  
  y_test <- read_csv(str_glue("./../../../mount_remote_phd/processed//",codename,"/",experiment_sha, "/",dataset_name,"/y_test.csv"))
  
  predictions <- results %>%
    filter(str_detect(measurementType, "predict"),
           experimentSha == experiment_sha,
           dataset==dataset_name)
  predictions$value <- map(predictions$value, jsonlite::fromJSON)
  
  predictions$auc <-map(predictions$value, compute_auc)
  predictions$roc <- map(predictions$value, compute_roc)
  
  predictions <- predictions %>% 
    rowwise() %>%
    mutate(
        sensitivities = list(roc$sensitivities),
       specificities = list(roc$specificities))
  
  
  aucs_file <- "./../../data/processed/aucs.csv"
  preds_to_write <- predictions %>%
    select(-value, 
           -sensitivities, 
           -specificities,
           -roc)
  preds_to_write$auc <- unlist(preds_to_write$auc)
  
  preds_to_write %>%
    glimpse
  if (!file.exists(aucs_file)) {
    # If the file doesn't exist, create a new file with just the new_data
    write.csv(preds_to_write, file = aucs_file, row.names = FALSE)
  } else {
    # Step 1: Read the original dataframe from the file
    original_df <- read.csv(aucs_file)
  
    # Step 3: Append the new dataframe to the original dataframe
    combined_df <- rbind(original_df, preds_to_write)
  
    # Step 4: Write the combined dataframe back to the original file
    write.csv(combined_df, file = aucs_file, row.names = FALSE)
  }
}
```
```{r}
all_results <- read.csv(aucs_file) %>%
  filter(dataset != "agaricus_lepiota")
```

```{r}
all_results %>%
  view("all")
```



```{r}
grouped <- all_results %>% group_by(
  dataset,
  measurementType
) %>%
  summarise(max_auc = max(auc),
            mean_auc = mean(auc),
            std_auc = sd(auc),
            n=n()) 

grouped <- grouped %>%
  group_by(dataset) %>%
  mutate(rank = rank(-max_auc),
         rank_mean = rank(-mean_auc))

grouped %>%
  
  arrange(dataset, -max_auc) %>%
  view("summary")
```

```{r}
grouped %>% 
  select(measurementType, dataset,max_auc) %>%
  mutate(max_auc = -max_auc) %>%
  pivot_wider(names_from = measurementType, values_from = max_auc) %>%
  write_csv(., "./../../data/processed/experiment_aucs.csv")

grouped %>% 
  select(measurementType, dataset,mean_auc) %>%
  mutate(mean_auc = -mean_auc) %>%
  pivot_wider(names_from = measurementType, values_from = mean_auc) %>%
  write_csv(., "./../../data/processed/experiment_aucs_mean.csv")
```



```{r}
grouped <- grouped %>%
  left_join(datasets_metadata, join_by(dataset==name)) %>%
  left_join(grouped %>%
    group_by(dataset) %>%
    summarise(best_auc = max(max_auc)) %>%
    mutate(difficulty = rank(best_auc)), 
    join_by(dataset==dataset)) %>%
  mutate(shortfall = max_auc-best_auc)



```



```{r}
predictions %>%
  glimpse
```

```{r}
grouped %>%
  glimpse

library(DescTools)

# boxplot(rank_mean ~ measurementType, data=grouped)

nemenyi_result_max <- NemenyiTest(rank ~ measurementType, data=grouped, method = "nemenyi")
nemenyi_result_mean <- NemenyiTest(rank_mean ~ measurementType, data=grouped, method = "nemenyi")


nemenyi_result_mean
nemenyi_result_max
```

```{r}
grouped %>%
  group_by(measurementType) %>%
  summarise(mean_rank = mean(rank))
```

```{r}
grouped %>%
  mutate(log_length = round(log(length))) %>%
  group_by(log_length, measurementType) %>%
  summarise(mean_rank = mean(rank)) %>%
  ggplot(aes(log_length, mean_rank, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point()
```

```{r}
grouped %>%
  mutate(round_width = round(width/5)*5) %>%
  group_by(round_width, measurementType) %>%
  summarise(mean_rank = mean(rank)) %>%
  ggplot(aes(round_width, mean_rank, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point() +
  xlim(0, 100)
```

```{r}
grouped %>%
  mutate(round_auc = round(max_auc/0.10)*10) %>%
  group_by(round_auc, measurementType) %>%
  summarise(mean_rank = mean(rank)) %>%
  ggplot(aes(round_auc, mean_rank, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point()
```
```{r}
grouped %>%
  view
```




```{r}
grouped %>%
  filter(measurementType %in% 
           c(
             "rf_predictions",
             "propneat_prediction",
             "propneat_retrain_prediction"
             # "nn_prediction",
             # "linear_regression_predictions"
             )) %>%
  ggplot(aes(difficulty, max_auc, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point() +
  ylim(0.5, 1) 
```

```{r}
grouped %>%
  filter(measurementType %in% 
           c(
             # "rf_predictions",
             # "propneat_prediction",
             "propneat_retrain_prediction",
             "linear_regression_predictions"
             # "nn_prediction"
             )) %>%
  ggplot(aes(difficulty, shortfall, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point()
```
```{r}
grouped %>%
  filter(measurementType %in% 
           c(
             # "rf_predictions",
             "propneat_prediction",
             # "propneat_retrain_prediction",
             "linear_regression_predictions"
             # "nn_prediction"
             )) %>%
  ggplot(aes(difficulty, shortfall, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point()
```
```{r}
grouped %>%
  filter(measurementType %in% 
           c(
             # "rf_predictions",
             "propneat_prediction",
             "propneat_retrain_prediction",
             "nn_prediction"
             # "linear_regression_predictions"
             )) %>%
  ggplot(aes(max_auc, mean_auc, group=measurementType, color=measurementType)) +
  geom_line() +
  geom_point()

```

```{r}

all_results %>% mutate(
  matched_run = round(iteration / 100) 
  ) %>% filter(
    dataset %in% c("breast_cancer", 
                   "dis",
                   "mushroom",
                   "churn",
                   "hypothyroid"),
  measurementType %in% c("propneat_prediction", "propneat_retrain_prediction")
) %>%
  ggplot(aes(measurementType, auc)) +
  geom_point() +
  facet_grid(dataset~matched_run)


all_results %>%
  group_by(dataset, measurementType) %>%
  summarise(n=n())
```

```{r}

```



Patricia Riddle to Everyone (27 Jul 2023, 10:34)
https://github.com/Didayolo/ranky
https://www.theoj.org/joss-papers/joss.02173/10.21105.joss.02173.pdf
 
Patricia Riddle to Everyone (27 Jul 2023, 10:40)
/https://www.jmlr.org/papers/volume7/demsar06a/demsar06a.pdf
Whenallclassifiersarecomparedwithacontrolclassifier,wecaninsteadoftheNemenyitest useoneofthegeneralproceduresforcontrollingthefamily-wiseerrorinmultiplehypothesistesting,suchastheBonferronicorrectionorsimilarprocedures.Althoughthesemethodsaregenerally conservativeandcanhavelittlepower,theyareinthisspecificcasemorepowerfulthantheNemenyitest,sincethelatteradjuststhecriticalvalueformakingk(k−1)/2comparisonswhilewhen comparingwithacontrolweonlymakek−1comparisons.
 
Patricia Riddle to Everyone (27 Jul 2023, 10:46)
https://search.r-project.org/CRAN/refmans/mlr/html/generateCritDifferencesData.html